The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2012-03-19 longRange.hetero/publish/main.tex
backup before improve theorem 1

The real and estimated error of the staggered mesh analytical
differentiation are presented in Fig.~\ref{fig:water-error}.  In this
case, due to the correlation of the charge positions, the assumption
of independent positions is disturbed, so all estimates overestimate
the real errors.
The error estimate of the staggered mesh analytical differentiation is 6.8 times
larger than the real error, which is not acceptable.
This means in the water system, the
positional correlation of charges plays a very important role
in the error estimate. More surprisingly, the correlation
actually reduces the error in force computation.
Currently we have no explaination for this phenomenon.
Anyway, the correlation error $\mathcal
E_{\textrm{correlation}}$ should be included to develop a more accurate error
estimate. 
By including the first neighbor approximation of the
correlation error, the error estimate is imporved greatly
(as indicated by the arrow in Fig.~\ref{fig:water-error}), and is only
twice as large as the real error.
This means among all atomic
correlates (i.e. the chemical bonds, the van der Waals interactions,
the hydrogen bonds, etc.), the first neighbor correlation (chemical bond)
is the most important one, and all
the rest account for the remaining discrepancy between the estimated and real
error.
The quality of the error estimate for the direct
part is still good (though not perfect): the error is overestimated by~50\%.
This indecates that the
first neigbor correlation is not that important in the error estimate of
the direct part.
Ref.~\cite{wang2010optimizing} showed that the error estimate that
is even three times larger than the real error
still works well in the parameter tuning process,
so the error estimate provided by the present paper is good enough
for the such practical applications.
% In this example, although both error estimates are
% not as sharp as the uncorrelated examples (Example 1 \& 2), they are
% good enough to derive for the parameter
% optimization~\cite{wang2010optimizing}.

@@

The effectivenss of the proposed error estimates was verified by
three numerical tests: two ideal inhomogeneous cases, in which the charges
are randomly distributed,
and one real water system, in which the charges are correlated.
In the ideal cases, the all error estimates are sharp, even in the extreme
case: positive and negative charges are globally seperated. 
In the water system,  all estimates overestimate the real error,
because of the correlation of charges.
The qulitity of  error estimates for the
real space  and the original SPME is acceptable.
However, the error estimate neglecting the charge correlation
is not applicable  for the staggered mesh Ewald method.
We included the correlation error by the first neighbor approximation,
and the 
the qulity of the
error estimate (of staggered mesh Ewald) was improved greatly.
This indicates among all possible correlations, the first
neighbor correlation is dominant.

>>>>

The real and estimated error of the staggered mesh analytical
differentiation are presented in Fig.~\ref{fig:water-error0}
and Fig.~\ref{fig:water-error}.  In this
case, due to the correlation of the charge positions, the assumption
of independent positions is disturbed, so all estimates overestimate
the real errors.
The quality of the direct
part errors estimates is still good (though not perfect):
the error is overestimated by~50\%.
The ik-differentiation error is overestimated by 2.6 times,
while the analytical differentiation error is overestimated by 4.7 times.
% This indecates that the
% first neigbor correlation is not that important in the error estimate of
% the direct part.
Ref.~\cite{wang2010optimizing} showed that the error estimate
(ik-differentiation in a homogeneous water system) that
is even three times larger than the real error
still works well in the parameter tuning process, so 
error estimate for the ik-differentiation is acceptable, but the error
estimate for the analytical differentiation is problematic.
The error estimate of the staggered mesh analytical differentiation is 6.8 times
larger than the real error,
which means the
positional correlation of charges plays a very important role
in the error estimate. More surprisingly, the correlation
actually greatly reduces the error in force computation.
Currently we have no explaination for this phenomenon.
Anyway, the correlation error $\mathcal
E_{\textrm{correlation}}$ should be included to develop a more accurate error
estimate. 
By including the first neighbor approximation of the
correlation error, the error estimate is imporved greatly
(as indicated by the arrow in Fig.~\ref{fig:water-error}), and is only
twice as large as the real error.
This means among all atomic
correlates (i.e. the chemical bonds, the van der Waals interactions,
the hydrogen bonds, etc.), the first neighbor correlation (chemical bond)
is the most important one, and all
the rest account for the remaining discrepancy between the estimated and real
error.
The error estimate for staggered mesh Ewald is now good enough
for the parameter tuning application.
% In this example, although both error estimates are
% not as sharp as the uncorrelated examples (Example 1 \& 2), they are
% good enough to derive for the parameter
% optimization~\cite{wang2010optimizing}.

@@

The effectivenss of the proposed error estimates was verified by
three numerical tests: two ideal inhomogeneous cases, in which the charges
are randomly distributed,
and one real water system, in which the charges are correlated.
In the ideal cases, the all error estimates are sharp, even in the extreme
case: positive and negative charges are globally seperated. 
In the water system,  all estimates overestimate the real error,
because of the correlation of charges.
The qulitity of  error estimates for the
real space  and the original ik-differentiation is acceptable.
However, the error estimate neglecting the charge correlation
is not applicable  for the staggered mesh Ewald method.
We included the correlation error by the first neighbor approximation,
and the 
the qulity of the
error estimate (of staggered mesh Ewald) was improved greatly.
This indicates among all possible correlations, the first
neighbor correlation is dominant.
